---
title: "EXOS Performance Evaluation"
author: "Egawati Panjei"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case

In this report, we generate 30 datasets for Case 1 (all data attributes have strong correlation) and Case 4 (all data attributes have weak correlation).
Dataset _i_ for each case is generated using the same seed random number. Hence, they have the same number of attributes in each group (stream). Each attribute j in Case 1 and Case 2 has similar mean and range. However, the mean and range of each attribute in each case is different. Cases 1 and 2 also have the same number of inlier and outlier data points. The difference is in their data attribute correlation.

## Case 1

```{r}
df_case1 = read.csv('dbpca/pickles/performance/small_cases/Case1/aggregate_3_1K_Case1_30.csv')
df_case1
```

## Case 4

```{r}
df_case4 = read.csv('dbpca/pickles/performance/small_cases/Case4/aggregate_3_1K_Case4_30.csv')
df_case4
```

# Precision

## Variance Test for Precision 
```{r}
var.test(df_case1$precision, df_case4$precision)
```

The var test shows that the true ratio of precision variances of Case 1 and Case 4 is equal to 1 (accept the null hypothesis). 

## t Test for Precision 
```{r}
t.test(df_case1$precision, df_case4$precision, alternative = "greater", var.equal=TRUE)
```
The t test shows that there is no difference between the precision mean of Case 1 and Case 4. We accept the null hypothesis. 

# Recall

## Variance Test for recall 
```{r}
var.test(df_case1$recall, df_case4$recall)
```

The var test shows that the true ratio of recall variances of Case 1 and Case 4 is equal to 1 (accept the null hypothesis). 


## t Test for recall 
```{r}
t.test(df_case1$recall, df_case4$recall, alternative = "greater", var.equal=TRUE)
```
The t test shows that there is no difference between the recall mean of Case 1 and Case 4. We accept the null hypothesis. 

# F1 score

## Variance Test for F1 score
```{r}
var.test(df_case1$f1_score, df_case4$f1_score)
```
The var test shows that the true ratio of f1 score variances of Case 1 and Case 4 is equal to 1 (accept the null hypothesis). 

## t Test for F1 score 
```{r}
t.test(df_case1$f1_score, df_case4$f1_score, alternative = "greater", var.equal=TRUE)
```
The t test shows that there is no difference between the F1 score mean of Case 1 and Case 4. We accept the null hypothesis since p-value is not small enough.  